Instructions for developing new pages for the MarineOmics webpage

### 2022-12-02 submissions_instructions.Rmd
Push Sam's formatting details for tables, citations, equations, and image insertions

---
title: 'Instructions for developing new pages for the MarineOmics webpage'
bibliography: RCN_site-Nov05.bib
---

@@

@@

````
```{r setup} `r ''`
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)

library(knitr)
library(knitcitations)
library(kableExtra)

knitr::opts_chunk$set(fig.width = 10, fig.height = 5) #setting the dimensions for figure outputs in a different line of code for cleanliness

cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc") #setting format for in-text citations for the references section at the bottom of the page
```
````
\* Note the "cache = " option. When set to "true" R will cache all of the output created from knitting the RMarkdown document. This is especially useful for pages with heavy computation that take a long time to knit.
<br>

### **formatting text**
Options abound for formatting text in .Rmd documents using [Pandoc Markdown](https://pandoc.org/MANUAL.html), and many of these can be found with a quick search, but we will go over a few basics here.

As with writing code, any text symbol that codes for something, such as a \# or a \* must be escaped with a backslash (\\) if you just want to use the symbol itself.

**\#**: *Outside of a code chunk*, pound signs dictate the size and organizational level of the text. A single \# will make large text and a main section in the navigation window. Two \#\# will make slightly smaller text and a sub-section in the navigation window. <br>

For example, the "RMarkdown formatting" text and category was created with "\# RMarkdown formatting" while the "code chunks" subcategory was created with "\#\# code chunks."

**\***: Asterisks are used to bold and italicize when surrounding texts. Use \*\***two asterisks to bold**\*\* and \**one asterisk*\* to italicize.

**\<br>**: adds a line break

**\<hr />**: adds a horizontal line across the page

### **installing & loading packages**
If you will be using any R packages for your information page or tutorial, it's a good idea to highlight them toward the beginning of your page, including code for installing them. Here's an example from the RADseq tutorial:

If you would like to run the R code examples that are scattered throughout the guide (recommended but not required!), you will need to install some R packages. Only need to run this code once:  
```{r, eval=F}
install.packages("tidyverse")
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
#the BiocManager package facilitates the installation of packages from the Bioconductor project
BiocManager::install("SeqArray")
BiocManager::install("SNPRelate")
```

### **caching**
If your page includes any code that takes a long time to run, please set "cache = TRUE" in the knitr::opts_chunk$set command in your global code chunk.

>>>>

---
title: "Instructions for developing new pages for the MarineOmics webpage"
bibliography: RCN_site-Nov05.bib
---

@@

### Example of table syntax

| Term A | Term B | Term C | Term D | Term E | Term F | Term G |
| :--- | :--- | :--- | :--- | :--- | :--- | :--- |
| xxx | xxx | xxx | xxx | xxx | xxx | xxx |  
| yyy | yyy | yyy | yyy | yyy | yyy | yyy | 
| zzz | zzz | zzz | zzz | zzz | zzz | zzz |

### Example of how to insert an image

```{r, echo = FALSE, out.height = "40%", fig.align = "center", }

knitr::include_graphics("images/Rivera_etal_fig.png")

```

### Example of how to write and print an equation

For illustrative purposes, here is a simple and famous equation

$$
E = mc^2
$$

As an example of a more complex equation, here is an equation for the t-statistic

$$
t = \frac{\overline{x_{1}}-\overline{x_{2}}}
{\sqrt{(s^2(
\frac{1}{n_{1}} + \frac{1}{n_{2}}
))}}
$$

### Example of how to cite a reference from your .bib in-text

RADseq can produce insightful analyses even in the absencee of data, if missing values are handled properly [@Tripp2017-cp].

@@

````
```{r setup} `r ''`
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE) 
library(knitr)
library(knitcitations)
library(kableExtra)
knitr::opts_chunk$set(fig.width = 10, fig.height = 5) #setting the dimensions for figure outputs in a different line of code for cleanliness
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc") #setting format for in-text citations for the references section at the bottom of the page
```
````
\* Note the "cache = " option. When set to "true" R will cache all of the output created from knitting the RMarkdown document. This is especially useful for pages with heavy computation that take a long time to knit.
<br>
### **formatting text**
Options abound for formatting text in .Rmd documents using [Pandoc Markdown](https://pandoc.org/MANUAL.html), and many of these can be found with a quick search, but we will go over a few basics here.
As with writing code, any text symbol that codes for something, such as a \# or a \* must be escaped with a backslash (\\) if you just want to use the symbol itself.
**\#**: *Outside of a code chunk*, pound signs dictate the size and organizational level of the text. A single \# will make large text and a main section in the navigation window. Two \#\# will make slightly smaller text and a sub-section in the navigation window. <br>
For example, the "RMarkdown formatting" text and category was created with "\# RMarkdown formatting" while the "code chunks" subcategory was created with "\#\# code chunks."
**\***: Asterisks are used to bold and italicize when surrounding texts. Use \*\***two asterisks to bold**\*\* and \**one asterisk*\* to italicize.
**\<br>**: adds a line break
**\<hr />**: adds a horizontal line across the page
### **installing & loading packages**
If you will be using any R packages for your information page or tutorial, it's a good idea to highlight them toward the beginning of your page, including code for installing them. Here's an example from the RADseq tutorial:
If you would like to run the R code examples that are scattered throughout the guide (recommended but not required!), you will need to install some R packages. Only need to run this code once:  
```{r, eval=F}
install.packages("tidyverse")
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
#the BiocManager package facilitates the installation of packages from the Bioconductor project
BiocManager::install("SeqArray")
BiocManager::install("SNPRelate")
```
### **caching**
If your page includes any code that takes a long time to run, please set "cache = TRUE" in the knitr::opts_chunk$set command in your global code chunk.
